Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-05-06 tese2/07_related_work_nat.tex
[RFT] related work nat  minor improvements

The need to build a global communications network in an age when almost nobody had access to that technology and the unpredictability of the number of future users, lead to some protocols not being suitable for the explosive growth and proliferation of users that followed. \ac{IPv4} limits the number of public addresses in such a way that today they are scarce \cite{ipv4}. {\color{blue} Today we live in the \emph{Internet of Things} era.
  Users and companies may have multiple devices that require Internet connectivity, such as personal computers, smart phones, tablets, traffic sensors, public vigillance systems, health monitoring tools and so on. All those devices combined cannot be publicly addressed by \ac{IPv4}.}
%RP vigillance -> surveilance?
%RP usa acrónimo IoT para Internet of Things

To this end, one way to overcome the \ac{IPv4} address scarcity problem was the development of a mechanism that groups multiple address into a single one, the machine that is assigned that address is then responsible for redirecting messages to members of its group using their private addresses, each connection in the private network is identified publicly by the same \ac{IP} address with a different port.
%RP o porto não identifica uma máquina (membro da rede privada) mas uma ligação.
This technique is known as \ac{NAT}.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\textwidth]{figures/nat.pdf}
	\caption{Network Address Translation}
\end{figure}
%RP na figura devias indicar que uns tem ips publicos e outros privados. Alternativamente, colocavas metade da nat box dentro da núvem para indicar que esta pertence à Internet e os pc não.

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.45\textwidth]{figures/multinat.pdf}
	\caption{Multiple level NATs}
\end{figure}

%RP file sharing não precisa de real-time
\ac{STUN} and \ac{TURN} \cite{natvoip} servers are a possible solution to overcome \ac{NAT}. None of those can establish direct connections on multiple level \ac{NAT}s.
%HR XXX I was here
%RP explicar o que são multiple level pois não falaste disto antes? São ``nested''?

>>>>

The need to build a global communications network in an age when almost nobody had access to that technology and the unpredictability of the number of future users, lead to some protocols not being suitable for the explosive growth and proliferation of users that followed. \ac{IPv4} limits the number of public addresses in such a way that today they are scarce \cite{ipv4}. {\color{blue} Today we live in the \ac{IoT} era.
  Users and companies may have multiple devices that require Internet connectivity, such as personal computers, smart phones, tablets, traffic sensors, public surveilance systems, health monitoring tools and so on. All those devices combined cannot be publicly addressed by \ac{IPv4}.}
%RP vigillance -> surveilance?
%RP usa acrónimo IoT para Internet of Things

To this end, one way to overcome the \ac{IPv4} address scarcity problem was the development of a mechanism that groups multiple address into a single one, the machine that is assigned that address is then responsible for redirecting messages to members of its group using their private addresses, each connection in the private network is identified publicly by the same \ac{IP} address with a different port.
%RP o porto não identifica uma máquina (membro da rede privada) mas uma ligação.
This technique is known as \ac{NAT} (figure \ref{fig:nat}).

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.7\textwidth]{figures/nat.pdf}
	\caption{Network Address Translation}
	\label{fig:nat}
\end{figure}
%RP na figura devias indicar que uns tem ips publicos e outros privados. Alternativamente, colocavas metade da nat box dentro da núvem para indicar que esta pertence à Internet e os pc não.

@@

\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.45\textwidth]{figures/multinat.pdf}
	\caption{Multiple level NATs}
	\label{fig:multinat}
\end{figure}

%RP file sharing não precisa de real-time
\ac{STUN} and \ac{TURN} \cite{natvoip} servers are a possible solution to overcome \ac{NAT}. None of those can establish direct connections on multiple level \ac{NAT}s (figure \ref{fig:multinat}).
%RP explicar o que são multiple level pois não falaste disto antes? São ``nested''?
